---
title: "Case Study 10: Building the Past"
author: "Joseph Borjon"
date: "July 2, 2018"
output:
  html_document:
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 12
    fig_width: 12
    fig_align: "center"
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::read_chunk("wrangle.r")
knitr::read_chunk("plot.r")
```

## A few related articles to remember

  * [Tidy spatial data in R: using `dplyr`, `tidyr`, and `ggplot2` with `sf`](http://strimas.com/r/tidy-sf)
  * [rnaturalearth](https://github.com/ropensci/rnaturalearth) (for plotting the whole world)
  * [geofacet](https://hafen.github.io/geofacet)

## Visualizing the mortgage crisis

```{r wrangle_data}
```

### Faceted change in construction by state

A crisp, concise way to show the construction dropoff in each state without overwhelming the eye. May require some explanation for the readers, but once they get it, they'll love it.

```{r plot_geofacet}
```

### Change in construction across years in the US

This chart shows the collapse as a gradual darkening of the land. Just another way to visualize the dropoff, complementary to the chart above, which is, in my opinion, more revealing.

```{r plot_us_evolution, fig.height=6}
```

### Idaho construction history

There is no better visualization for looking at historical shape of construction data than the line chart. A colored map wouldn't do this data justice.

```{r plot_idaho_permits}
```
