---
title: "Task 6: World Data Investigation"
author: "Joseph Borjon"
date: "July 16, 2018"
output:
  html_document:
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: "center"
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::read_chunk("plot.r")
```
## WHO suicide rates plot recreation from [*Our World in Data*](https://ourworldindata.org/suicide)

In general, it cannot be said that, based on these countries, the world has made a whole lot of progress in reducing suicide rates since 1950. The US and Sweden show the most apparent progress. Perhaps the same can be said of Russia after its spike in the 1990s; I'd like to know what happened in Russia in the mid-1980s that reduced suicide rates so dramatically.

```{r plot_suicide}
```



## Child mortality over time across continents

The foillowing chart shows what a dramatic difference humanity has been able to effect in the last 200 years regarding child mortality rates: its average has been steadily reduced in every continent. More work needs to be done in Africa, but look how far it has come.

```{r plot_child_mortality}
```
