---
title: "Case Study 9: Interacting with time"
author: "Joseph Borjon"
date: "June 25, 2018"
output:
  html_document:
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: "center"
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::read_chunk("wrangle.R")
knitr::read_chunk("plot-closing-prices.R ")
knitr::read_chunk("plot-price-vs-volume.R")
```

```{r wrangle}
```

## Five-year closing price history

The following charts show the closing price for each stock every trading day for the last 5 years. The price scale goes from 0 to the maximum price in the entire dataset to ensure a common y-axis scale.

```{r plot_closing_prices}
```

## Does a higher trading volume produce a lower stock price?

The following chart uses the same 5-year history data to visualiize the correlation between trading volume and stock price. Closing prices were used for this chart as well.

```{r plot_price_vs_volume, fig.height=24}
```
