---
title: "Task 14: Counting Words and Occurrences"
author: "Joseph Borjon"
date: "June 7, 2018"
output:
  html_document:
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: "center"
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::read_chunk("word-summaries.r")
knitr::read_chunk("bofm-word-dist-by-verse.r")
```

```{r word_summaries}
```

## Average verse lengths in the New Testament and the Book of Mormon

According to the output of my R script, verses in the **New Testament** contain an average of 22.71 words, while verses in **The Book of Mormon** contain nearly double that amount, at 40.51 words.

## Instances of the word "Jesus" in the New Testament and the Book of Mormon

The word "Jesus" appears 7,957 times in the **New Testament** out of a total of 180,665 words, and 6,604 times in **The Book of Mormon** out of a total 267,519 of words. This may not be a good metric, since the Savior is referred to by many other names in all books of scripture.

## Word counts in each Book of Mormon verse

```{r bofm_word_dist_by_verse}
```
