---
title: "Does Public Education Quality Affect Students' Suicide Rates?"
author: "Joseph Borjon"
date: "July 23, 2018"
output:
  html_document:
    keep_md: true
    code_folding: hide
    fig_height: 12
    fig_width: 12
    fig_align: "center"
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::read_chunk("us-education-data.R")
knitr::read_chunk("combined-data.R")
knitr::read_chunk("plot.R")
```

```{r pull_education_data}
```

```{r combine_data}
```

```{r prepare_to_plot}
```


## Introduction

Does the quality of public education affect the rate at which students commit suicide? If not, what other variables could be at play?

To explore potential answers to those questions, let's examine the data provided by the Stanford Center for Education Policy Analysis against suicide data from the CDC.

Test scores from the EdFacts federal initiative are used as proxy for public education quality. The Standford dataset included some county socioeconomic data, which will likewise be used. The CDC data includes only counts of completed, not attempted, suicides per county. How many attempted suicides resulted in non-death is unknown. No known suicides were committed in the United States under the age of 10, according to the data.

Data are averaged across years to facilitate visualization, since the exploration focuses on long-term trends. A more granular analysis including time-series visualizations and other data, possibly encompassing weather and additional socioeconomic factors, is a project for a future time; after all, there are only so many days in one semester.

To see a summary plot of all the used variables, see near the end.


## So, what's the answer?

Seeing the counties where school-age children committed suicide, at at what rates, should begin to answer the question:

```{r plot_child_suicides}
```


And this is how schools fared in terms of quality:

```{r plot_education_results}
```


The South and Southwest seem to have the lowest achievement scores. While the distribution and rates of adult suicides seem to follow a similar trend (which could be due to any number of confounding variables), the corresponding variables for school-age children do not strongly follow the same pattern. There are notable exceptions in Florida and two counties in northeast Arizona, and there *are* more filled counties in and around the South and Southwest than anywhere else.

For comparison, the 20-and-above group (a much larger cohort, and therefore much more widespread) committed suicide in the following locations:

```{r plot_adult_suicides}
```


Notice that, at first glance, it appears that older people commit suicide at higher rates than school-age children, but, in general, the difference is not abysmal.


## What other variables could be at play, then?

I'm glad you asked. Two variables that come to mind, and are serendipitously provided by Stanford, are poverty and unemployment.

Starting with poverty:

```{r plot_household_poverty}
```


From the data, there is no way to know how far below the poverty line the households in question are. All we know is the percentage of households that fall below the line, which should be a good-enough measure.


Now, onto unemployment:

```{r plot_unemployment}
```


Again, the South and Southwest have the least to boast about regarding children household poverty and unemployment.

Notice the strip of lower suicide rates running roughly down the Midwest, from North Dakota to Texas. That same area has higher employment rates. Anecdotally, the Midwest has a relatively low-stress lifestyle and large areas that are free of visual clutter and full of nature. Even Omaha, a large city, has decent traffic. And there is a large religious influence in the area, from what I hear; people of faith with less hipocrisy than in, shall we say, other places.


## Can we see how these variables are interrelated? It's hard to keep scrolling up and down

Sure. Here you go:

```{r plot_education_scatterplot}
```


By looking at states with higher point counts (such as California, Texas, Colorado, and North Carolina), it is quite evident that poverty and unemployment tend to be higher at the lower part of the facet, where test results are lower. However, increase of suicide rates happens inconsistenly, not necessarily at the bottom, with Arizona, again, as a notable exception.


## Conclusion

Rather than trying to figure out which one, if any, of these variables causes the others (which is likely impossible to know for certain, as I learned in my anthropology studies), it is more astute to conclude that quality of education, poverty, and unemployment are interrelated variables that feed each other. Causes may be historical, geographical, geopolitical, psychological, and so forth, but seeing correlations can be invaluable indeed.

In other words, there is no conclusive evidence that quality of education in terms of scores influences suicide rates among children, but other factors may: diet, altitude, depression rates, lifestyle, parental stress, level of career demands, traffic, etc. Unemployment level does seem to be highly correlated.

Other school-related variables, unavailable at present, may indeed affect students' suicide rates: quality of administration, presence and quality of organizational support systems for students, cognitive disability rates, etc.

While we don't have all the answers, we do need to understand that each suicide is a valuable life ended, and that we need to do all we can at the personal, family, intitution, and government levels to help reduce suicide rates throughout the United States and the world. Each life counts.


## Sources

  * [CDC WISQARS](https://wisqars.cdc.gov:8443/cdcMapFramework/mapModuleInterface.jsp)

  * Sean F. Reardon, Andrew D. Ho., Benjamin R. Shear, Erin M. Fahle, Demetra Kalogrides, & Richard DiSalvo. (2018). Stanford Education Data Archive (Version 2.1). http://purl.stanford.edu/db586ns4974.
